Syntax and Semantics of Abstract Binding Trees

### 2015-11-11 paper.tex
[paper] improve interpretation diagrams

The construction of $\beta$ proceeds by renaming the parameters of the operator
$\vartheta$ and constructing the (bound) arguments $\gamma$ of the operator.
\[
  \begin{tikzcd}[cramped, ampersand replacement = \&]
    {\IMode{\SemBrackets{\Omega\triangleright\Upsilon\parallel\Gamma}_P}}
       \arrow[r, "\Define{\beta\,}{\,\Tuple{\SemBrackets{\vartheta}_P, \gamma}}"]
    \&[3.0em] {\IMode{%
       \coprod_{\vartheta\in \Operators_{\MkArity{\vec{v}}{\tau}}}%
       \prod_{\MkValence{\vec{\sigma}_i}{\vec{\tau}_i}{\tau_i}\in\vec{v}}%
       P_{\tau_i}^{\Yoneda{\vec{\sigma}_i\parallel\vec{\tau}_i}}%
    }}
  \end{tikzcd}
\]
Each argument
%
\begin{tikzcd}[cramped, ampersand replacement = \&]
  {\IMode{\SemBrackets{\Omega\triangleright\Upsilon\parallel\Gamma}_P}}
    \arrow[r, "\IMode{\gamma_i}"]
  \& {\IMode{%
    P_{\tau_i}^{\Yoneda{\vec{\sigma}_i\parallel\vec{\tau}_i}}
  }}
\end{tikzcd}
%
is the exponential transpose of the composite,
\[
  \begin{tikzcd}[cramped, ampersand replacement = \&]
    {\IMode{\SemBrackets{\Omega\triangleright\Upsilon\parallel\Gamma}_P
       \times\Yoneda{\vec{\sigma}_i\parallel\vec{\tau}_i}
    }}
      \arrow[r, "\IMode{\Tuple{\pi_1\circ\pi_1,\phi_i,\psi_i}}"]
    \&[4.0em] {\IMode{\SemBrackets{\Omega\triangleright\Upsilon,\vec{\sigma}_i\parallel\Gamma,\vec{\tau}_i}_P}}
      \arrow[r, "\IMode{\SemBrackets{\Omega\triangleright\Upsilon,\vec{\sigma}_i\parallel\Gamma,\vec{\tau}_i\vdash M_i:\tau_i}_P}"]
    \&[7.5em] {\IMode{P_{\tau_i}}}
  \end{tikzcd}
\]
where $\phi_i,\psi_i$ are defined as follows:
\begin{gather*}
  \begin{tikzcd}[cramped, ampersand replacement = \&]
    {\IMode{\SemBrackets{\Omega\triangleright\Upsilon\parallel\Gamma}_P
       \times\Yoneda{\vec{\sigma}_i\parallel\vec{\tau}_i}
    }}
      \arrow[r, "\Define{\phi_i\,}{\,\Tuple{\pi_u\circ\pi_1}_{u\in\Dom{\Upsilon}},\, \Tuple{\pi_u\circ\pi_1\circ\pi_2}_{u\in\Dom{\vec{\sigma}_i}}}"]
    \&[12.0em] {\IMode{S^{\{\Upsilon,\vec{\sigma}_i\}}}}\\[-1.0em]
    {\IMode{\SemBrackets{\Omega\triangleright\Upsilon\parallel\Gamma}_P
       \times\Yoneda{\vec{\sigma}_i\parallel\vec{\tau}_i}
    }}
      \arrow[r, "\Define{\psi_i\,}{\,\Tuple{\pi_x\circ\pi_1}_{x\in\Dom{\Gamma}},\, \Tuple{\pi_x\circ\pi_1\circ\pi_2}_{x\in\Dom{\vec{\tau}_i}}}"]
    \&[12.0em] {\IMode{V^{[\Gamma,\vec{\tau}_i]}}}
  \end{tikzcd}
\end{gather*}

>>>>

The construction of $\beta$ proceeds by renaming the parameters of the operator
$\vartheta$ and constructing the (bound) exponentiated arguments $\gamma$ of the
operator.
\[
  \begin{tikzcd}[cramped, ampersand replacement = \&]
    {\IMode{\SemBrackets{\Omega\triangleright\Upsilon\parallel\Gamma}_P}}
       \arrow[r, "\Define{\beta\,}{\,\Tuple{\SemBrackets{\vartheta}_P, \lambda\gamma}}"]
    \&[4.0em] {\IMode{%
       \coprod_{\vartheta\in \Operators_{\MkArity{\vec{v}}{\tau}}}%
       \prod_{\MkValence{\vec{\sigma}_i}{\vec{\tau}_i}{\tau_i}\in\vec{v}}%
       P_{\tau_i}^{\Yoneda{\vec{\sigma}_i\parallel\vec{\tau}_i}}%
    }}
  \end{tikzcd}
\]
Argument $\lambda\IMode{{\gamma}_{i}}$ are the exponential transposes (curried
form) of the composites $\IMode{{\gamma}_{i}}$:
\[
  \begin{tikzcd}[cramped, ampersand replacement = \&]
    {\IMode{\SemBrackets{\Omega\triangleright\Upsilon\parallel\Gamma}_{P}}}
      \arrow[d, dashed, swap, "\IMode{\lambda{\gamma}_{i}}"]
    \&
    {\IMode{\SemBrackets{\Omega\triangleright\Upsilon\parallel\Gamma}_{P}
       \times\Yoneda{\vec{\sigma}_{i}\parallel\vec{\tau}_{i}}}
    }
      \arrow[r, "\IMode{\Tuple{{\pi}_{[1,1]},{\phi}_{i},{\psi}_{i}}}"]
      \arrow[d, dashed, swap, "\IMode{{\gamma}_{i}}"]
    \&[3.5em]
    {\IMode{\SemBrackets{\Omega\triangleright\Upsilon,\vec{\sigma}_i\parallel\Gamma,\vec{\tau}_{i}}_{P}}}
      \ar{dl}[
        , rotate = +19.25
        , xshift = -4.5em
        , yshift = -0.2em
      ]{\IMode{\SemBrackets{\Omega\triangleright\Upsilon,\vec{\sigma}_{i}\parallel\Gamma,\vec{\tau}_{i}\vdash M_i:\tau_i}_P}}
    \\[2.0em]
    {\IMode{{P}_{{\tau}_{i}}^{\Yoneda{\vec{\sigma}_{i}\parallel\vec{\tau}_{i}}}}}
    \& {\IMode{P_{{\tau}_{i}}}}
    \&
  \end{tikzcd}
\]
where $\phi_i,\psi_i$ are defined as follows:
\begin{gather*}
  \begin{tikzcd}[cramped, ampersand replacement = \&]
    {\IMode{\SemBrackets{\Omega\triangleright\Upsilon\parallel\Gamma}_P
       \times\Yoneda{\vec{\sigma}_i\parallel\vec{\tau}_i}
    }}
      \arrow[r, "\Define{\phi_i\,}{\,\Pair{\Tuple{\pi_u\circ\pi_1}_{u\in\Dom{\Upsilon}}}{\,\Tuple{\pi_u\circ\pi_{[2,1]}}_{u\in\Dom{\vec{\sigma}_i}}}}"]
    \&[12.0em] {\IMode{S^{\{\Upsilon,\vec{\sigma}_i\}}}}\\[-1.0em]
    {\IMode{\SemBrackets{\Omega\triangleright\Upsilon\parallel\Gamma}_P
       \times\Yoneda{\vec{\sigma}_i\parallel\vec{\tau}_i}
    }}
      \arrow[r, "\Define{\psi_i\,}{\,\Pair{\Tuple{\pi_x\circ\pi_1}_{x\in\Dom{\Gamma}}}{\,\Tuple{\pi_x\circ\pi_{[2,1]}}_{x\in\Dom{\vec{\tau}_i}}}}"]
    \&[12.0em] {\IMode{V^{[\Gamma,\vec{\tau}_i]}}}
  \end{tikzcd}
\end{gather*}
